ML comparison

### 2020-10-12 src/s_ar1.Rmd
added lots of things ml-related

nreplicates <- 1000
r_star_vals <- vector(length = nreplicates)
r_hat_vals <- vector(length = nreplicates)
for(i in 1:nreplicates){
  if(i%%100==0)
    print(i)

@@

saveRDS(tibble(r_star=r_star_vals, r_hat=r_hat_vals), "../data/ar1_r_star_hat.rds")
```

Plot results
```{r}
reses <- readRDS("../data/ar1_r_star_hat.rds")
r_star_vals <- reses$r_star 
r_hat_vals <- reses$r_hat 
g2 <- tibble(accuracy=r_star_vals, iteration=seq(1, nreplicates, 1)) %>% 
  ggplot(aes(x=accuracy)) +
  geom_histogram() +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  ggtitle("B.") +
  theme(text = element_text(size=18, colour="black"),
        axis.text = element_text(colour="black", size=16)) +
  xlim(0.9, NA)

@@

caretGrid <- expand.grid(interaction.depth=c(3), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)

rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "gbm",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid, verbose=FALSE)

@@

# Show performance as a function of hyperparameters
```{r}
caretGrid <- expand.grid(interaction.depth=c(3), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid1 <- expand.grid(interaction.depth=c(5), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid2 <- expand.grid(interaction.depth=c(3), n.trees = 100,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid3 <- expand.grid(interaction.depth=c(5), n.trees = 100,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid4 <- expand.grid(interaction.depth=c(7), n.trees = 100,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
caretGrid5 <- expand.grid(interaction.depth=c(7), n.trees = 200,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
lgrids <- list(caretGrid, caretGrid1, caretGrid2, caretGrid3, caretGrid4, caretGrid5)
f_replicate_hyper <- function(lgrids){
  temp <- f_generate_lower_var_four(1/3, 0.3, 1, 1000)
  a_array <- array(dim=c(1000, 4, 1))
  a_array[,,1] <- temp
  laccuracy <- vector(length = length(lgrids))
  for(i in seq_along(lgrids))
    laccuracy[i] <- r_star(a_array, caret_default=lgrids[[i]])
  return(laccuracy)
}

nreplicates <- 200
r_star_vals <- matrix(nrow = nreplicates, ncol=length(lgrids))
for(i in 1:nreplicates){
  if(i%%100==0)
    print(i)

  temp <- f_replicate_hyper(lgrids)
  r_star_vals[i, ] <- temp
}

saveRDS(r_star_vals, "../data/ar1_sensitivity.rds")
r_star_vals <- readRDS("../data/ar1_sensitivity.rds")

b_sum <-
  r_star_vals %>% 
  as.data.frame() %>% 
  mutate(iterate=seq(1, nreplicates, 1)) %>%
  melt(id.vars="iterate") %>% 
  mutate(below=if_else(value < 1, 1, 0)) %>% 
  group_by(variable) %>% 
  summarise(below_per=round(mean(below)*100, 1),
            lower=quantile(value, 0.25),
            upper=quantile(value, 0.75),
            middle=median(value)) %>%
  mutate(below_per=paste0(below_per, "%")) %>% 
  mutate(variable=case_when(variable=="V1"~"int.depth=3\nn.trees=50",
                            variable=="V2"~"int.depth=5\nn.trees=50",
                            variable=="V3"~"int.depth=3\nn.trees=100",
                            variable=="V4"~"int.depth=5\nn.trees=100",
                            variable=="V5"~"int.depth=7\nn.trees=100",
                            variable=="V6"~"int.depth=7\nn.trees=200")) %>% 
  arrange(variable) %>% 
  mutate(x_pos=seq(1, 6, 1)) %>% 
  mutate(y_pos=0.95)

g <- r_star_vals %>% 
  as.data.frame() %>% 
  mutate(iterate=seq(1, nreplicates, 1)) %>% 
  melt(id.vars="iterate") %>% 
  mutate(below=if_else(value < 1, 0, 1)) %>% 
  mutate(variable=case_when(variable=="V1"~"int.depth=3\nn.trees=50",
                            variable=="V2"~"int.depth=5\nn.trees=50",
                            variable=="V3"~"int.depth=3\nn.trees=100",
                            variable=="V4"~"int.depth=5\nn.trees=100",
                            variable=="V5"~"int.depth=7\nn.trees=100",
                            variable=="V6"~"int.depth=7\nn.trees=200")) %>% 
  left_join(b_sum, by = "variable") %>%
  ggplot(aes(x=as.factor(variable), y=value, colour=as.factor(below))) +
  geom_jitter() +
  xlab("Hyperparameters") +
  ylab("R*") +
  geom_hline(yintercept = 1, linetype=2) +
  annotate("text", x = b_sum$x_pos, y = b_sum$y_pos, label = b_sum$below_per, size=6) +
  annotate("pointrange", x = 1:6, ymin=b_sum$lower, ymax=b_sum$upper, y = b_sum$middle, colour="black", size=1) +
  coord_flip() +
  scale_color_grey() +
  theme(axis.text = element_text(colour="black", size=16),
        axis.title = element_text(colour="black", size=20),
        legend.position = "none")
ggsave("../output/ar1_sensitivity.pdf", g, width = 12, height = 8)
```

>>>>

nreplicates <- 100
r_star_vals <- vector(length = nreplicates)
r_hat_vals <- vector(length = nreplicates)
for(i in 1:nreplicates){
    print(i)

@@

# saveRDS(tibble(r_star=r_star_vals, r_hat=r_hat_vals), "../data/ar1_r_star_hat.rds")
```

Plot results
```{r}
# reses <- readRDS("../data/ar1_r_star_hat.rds")
r_star_vals <- reses$r_star 
r_hat_vals <- reses$r_hat 
g2 <- tibble(accuracy=r_star_vals, iteration=seq(1, nreplicates, 1)) %>% 
  ggplot(aes(x=accuracy)) +
  geom_histogram() +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  ggtitle("B.") +
  theme(text = element_text(size=18, colour="black"),
        axis.text = element_text(colour="black", size=16)) +
  xlim(0.9, NA)

@@

caretGrid <- tibble(mtry=2)

rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "rf",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid, verbose=FALSE)

@@

### 2020-10-12 src/s_cauchy.Rmd
added lots of things ml-related

a_df <- 
  tibble(iteration=iter,
         alt=laccuracy1,
       nom=laccuracy)
# saveRDS(a_df, "../output/cauchy_r_star.rds")
```

```{r}
a_df <- readRDS("../output/cauchy_r_star.rds")
g2 <- 
  a_df %>% 
  melt(id.vars="iteration") %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_grey("Parameterisation", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.8, 0.7),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black"),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("D. Split-$R^*$"))
g2
```

>>>>

a_df <- 
  tibble(iteration=iter,
         alt=laccuracy1,
       nom=laccuracy)
saveRDS(a_df, "../output/cauchy_r_star_rf.rds")
```

```{r}
# a_df <- readRDS("../output/cauchy_r_star.rds")
g2 <- 
  a_df %>% 
  melt(id.vars="iteration") %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_grey("Parameterisation", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.8, 0.7),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black"),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("D. Split-$R^*$"))
g2
```

Add in GBM R*
```{r}
a_df <- readRDS("../output/cauchy_r_star.rds") %>% 
  mutate(model="gbm")
a_df1 <- readRDS("../output/cauchy_r_star_rf.rds") %>% 
  mutate(model="rf")
g2 <- a_df %>%
  bind_rows(a_df1) %>% 
  melt(id.vars=c("iteration", "model")) %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable), linetype=as.factor(model))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_grey("Parameterisation", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black"),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("D. Split-$R^*$"))+
  scale_linetype_discrete("Model") +
  guides(colour = guide_legend(nrow = 1, byrow = T),
         linetype=guide_legend(nrow = 1, byrow = T))
ggsave("../output/fig_9d.pdf", g2, width = 12, height = 8)
```

### 2020-10-12 src/s_eight_schools.Rmd
added lots of things ml-related

Plot two R* distributions
```{r}
g1 <- 
  c_df %>% 
  melt(id.vars=c("metric", "simulations")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  xlim(0.78, 1.6) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("A.") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = "none")
g2 <- 
  d_df %>% 
  melt(id.vars=c("metric", "simulations")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlim(0.78, 1.6) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("B.") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = "none")
# a_df <- readRDS("../output/eight_schools_replicates_4_index.rds")
```

@@

pdf("../output/eight_schools.pdf", width = 12, height = 4)
multiplot(g1, g2, g3, cols = 3)
dev.off()
```

# Plot R* versus quantiles
```{r}
x <- rstan::extract(fit_cp, permuted=F)
g1 <- plot_r_star_quantiles(1, x, nsim=40, split_chains = F) +
  scale_y_continuous(limits = c(0.6, 1.7), breaks = c(0.6, 0.8, 1, 1.2, 1.4, 1.6)) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank()) +
  coord_flip()

g2 <- plot_r_star_quantiles(2, x, nsim=40, split_chains = F) +
  scale_y_continuous(limits = c(0.6, 1.7), breaks = c(0.6, 0.8, 1, 1.2, 1.4, 1.6)) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  coord_flip()

@@

pdf("../output/eight_schools_r_star_quantiles1.pdf", width = 6, height = 4)
plot_grid(gb, g1, ga, g2, nrow = 2, rel_widths = c(1, 0.4), rel_heights = c(0.9, 1))
dev.off()
```

>>>>

Plot two R* distributions
```{r}
g1 <- 
  c_df %>% 
  melt(id.vars=c("metric", "simulations")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  xlim(0.78, 2) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("A.") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = "none")
g2 <- 
  d_df %>% 
  melt(id.vars=c("metric", "simulations")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlim(0.78, 2) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("B.") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = "none")
# a_df <- readRDS("../output/eight_schools_replicates_4_index.rds")
```

@@

pdf("../output/fig_10.pdf", width = 12, height = 4)
multiplot(g1, g2, g3, cols = 3)
dev.off()
```

# Plot R* versus quantiles
```{r}
x <- rstan::extract(fit_cp, permuted=F)
g1 <- plot_r_star_quantiles(1, x, nsim=40, split_chains = F) +
  scale_y_continuous(limits = c(0.6, 2.6)) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank()) +
  coord_flip()

g2 <- plot_r_star_quantiles(2, x, nsim=40, split_chains = F) +
  scale_y_continuous(limits = c(0.6, 2.6)) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  coord_flip()

@@

pdf("../output/fig_11.pdf", width = 6, height = 4)
plot_grid(gb, g1, ga, g2, nrow = 2, rel_widths = c(1, 0.4), rel_heights = c(0.9, 1))
dev.off()
```

### 2020-10-12 src/s_hyperparameters.Rmd
added lots of things ml-related

saveRDS(r_star_vals, "../data/ar1_sensitivity.rds")
r_star_vals <- readRDS("../data/ar1_sensitivity.rds")

b_sum <-
  r_star_vals %>% 
  as.data.frame() %>% 
  mutate(iterate=seq(1, nreplicates, 1)) %>%
  melt(id.vars="iterate") %>% 
  mutate(below=if_else(value < 1, 1, 0)) %>% 
  group_by(variable) %>% 
  summarise(below_per=round(mean(below)*100, 1),
            lower=quantile(value, 0.25),
            upper=quantile(value, 0.75),
            middle=median(value)) %>%
  mutate(below_per=paste0(below_per, "%")) %>% 
  mutate(x_pos=seq(1, nrow(m_parameters), 1)) %>% 
  mutate(y_pos=0.95)

g <- b_sum %>% 
  cbind(m_parameters) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.98, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
ggsave("../output/ar1_sensitivity.pdf", g, width = 12, height = 8)
```

@@

r_star_vals %>% 
  melt(id.vars=c("n.trees", "int.depth")) %>% 
  group_by(n.trees, int.depth) %>% 
  summarise(lower=quantile(value, 0.25),
            upper=quantile(value, 0.75),
            middle=median(value)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.98, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
```

@@

m_parameters <- expand_grid(int.depth=c(3, 7, 11),
                            n.trees=c(50, 100, 400))
r_star_vals <- f_replicate_r_star(2, m_parameters, f_data_cauchy)
```

>>>>

# saveRDS(r_star_vals, "../data/ar1_sensitivity.rds")
g <- readRDS("../data/hypers_ar1.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.98, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
ggsave("../output/hypers_ar1.pdf", g, width = 12, height = 8)
```

@@

readRDS("../data/hypers_8_schools.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
```

@@

m_parameters <- expand_grid(int.depth=c(3, 7, 11),
                            n.trees=c(50, 100, 400))
r_star_vals <- f_replicate_r_star(2, m_parameters, f_data_cauchy)

readRDS("../data/hypers_cauchy.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
```

# RF hyperparameters
AR1
```{r}
temp <- readRDS("../data/hypers_rf_ar1.rds")$r_star
temp %>%
  melt(id.vars="mtry") %>%
  group_by(mtry) %>%
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>%
  ggplot(aes(x=as.factor(mtry), y=middle)) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# features") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
```

8 schools
```{r}
temp <- readRDS("../data/hypers_rf_8_schools.rds")$r_star
temp %>%
  melt(id.vars="mtry") %>%
  group_by(mtry) %>%
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>%
  ggplot(aes(x=as.factor(mtry), y=middle)) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# features") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
```
Cauchy
```{r}
temp <- readRDS("../data/hypers_rf_cauchy.rds")$r_star
temp %>%
  melt(id.vars="mtry") %>%
  group_by(mtry) %>%
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>%
  ggplot(aes(x=as.factor(mtry), y=middle)) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# features") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
```

Normal
```{r}
temp <- readRDS("../data/hypers_rf_")$r_star
temp %>%
  melt(id.vars="mtry") %>%
  group_by(mtry) %>%
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>%
  ggplot(aes(x=as.factor(mtry), y=middle)) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# features") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T))
```

# xgbtree
AR1
```{r}
temp <- readRDS("../data/hypers_xgbtree_ar1.rds")$r_star
temp %>%
  select(-one_of("gamma", "colsample_bytree", "min_child_weight", "subsample")) %>% 
  melt(id.vars=c("nrounds", "max_depth", "eta")) %>%
  group_by(nrounds, max_depth, eta) %>%
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>%
  ggplot(aes(x=as.factor(nrounds), y=middle, colour=as.factor(max_depth), group=as.factor(max_depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# rounds") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black")) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  facet_wrap(~eta)
```

```{r}
temp <- readRDS("../data/hypers_xgbtree_8_schools.rds")$r_star
temp %>%
  select(-one_of("gamma", "colsample_bytree", "min_child_weight", "subsample")) %>% 
  melt(id.vars=c("nrounds", "max_depth", "eta")) %>%
  group_by(nrounds, max_depth, eta) %>%
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>%
  ggplot(aes(x=as.factor(nrounds), y=middle, colour=as.factor(max_depth), group=as.factor(max_depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line() +
  xlab("# rounds") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black")) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  facet_wrap(~eta)
```

### 2020-10-12 src/s_ml.Rmd
added lots of things ml-related

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_ar1)
temp_df <- readRDS("../data/ml_comp_hypers_set_ar1.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
```

@@

temp_df <- readRDS("../data/ml_comp_hypers_set_8_schools.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
temp_df %>%
  ggplot(aes(x=time, y=r_star, colour=as.factor(method))) +
  geom_jitter()
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_cauchy)
temp_df <- readRDS("../data/ml_comp_hypers_set_cauchy.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
temp_df %>%
  ggplot(aes(x=time, y=r_star, colour=as.factor(method))) +
  geom_jitter()
```

@@

temp_df <- readRDS("../data/ml_comp_hypers_set_normal_250.rds")
temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot()
temp_df %>%
  ggplot(aes(x=as.factor(method), y=time)) +
  geom_boxplot()

temp_df %>%
  ggplot(aes(x=time, y=r_star, colour=as.factor(method))) +
  geom_jitter()
```

>>>>

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_ar1)

temp_df <- readRDS("../data/ml_comp_hypers_set_ar1.rds") %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, orders))
g1 <- temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("R*") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  ggtitle("A.")
g2 <- temp_df %>%
  ggplot(aes(x=as.factor(method), y=time)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("Time") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  ggtitle("B.")
pdf("../output/ml_comparison_ar1.pdf", width = 12, height = 8)
multiplot(g1, g2, cols = 2)
dev.off()
```

@@

temp_df <- readRDS("../data/ml_comp_hypers_set_8_schools.rds") %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, orders))
g1 <- temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("R*") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  ggtitle("A.")
g2 <- temp_df %>%
  ggplot(aes(x=as.factor(method), y=time)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("Time") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  ggtitle("B.")
pdf("../output/ml_comparison_8_schools.pdf", width = 12, height = 8)
multiplot(g1, g2, cols = 2)
dev.off()
```

@@

temp_df <- f_run_all_replicates(2, c("gbm", "rf", "knn", "svmLinear", "multinom"),
          list(tunegrid_gbm, tunegrid_rf, tunegrid_knn, tunegrid_svm, tunegrid_multinom),
          f_data_cauchy)
temp_df <- readRDS("../data/ml_comp_hypers_set_cauchy.rds") %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, orders))
g1 <- temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("R*") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  ggtitle("A.")
g2 <- temp_df %>%
  ggplot(aes(x=as.factor(method), y=time)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("Time") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  ggtitle("B.")
pdf("../output/ml_comparison_cauchy.pdf", width = 12, height = 8)
multiplot(g1, g2, cols = 2)
dev.off()
```

@@

orders <- c("rf", "xgbTree", "gbm", "knn", "multinom", "svmLinear")

temp_df <- readRDS("../data/ml_comp_hypers_set_normal_250.rds") %>% 
  mutate(method=as.factor(method)) %>% 
  mutate(method=fct_relevel(method, orders))
g1 <- temp_df %>%
  ggplot(aes(x=as.factor(method), y=r_star)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("R*") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  ggtitle("A.")
g2 <- temp_df %>%
  ggplot(aes(x=as.factor(method), y=time)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("Time") +
  theme(text=element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.83, 0.79),
        legend.text = element_text(size=12, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  ggtitle("B.")
pdf("../output/ml_comparison_mvt_normal_250.pdf", width = 12, height = 8)
multiplot(g1, g2, cols = 2)
dev.off()
```
